Automated Topic Naming

### 2011-09-03 ese/ese.tex
why did this take so much time?

In Figure \ref{fig:authorcluster} we clustered developers using the
Ward method of Hierarchical clsutering. We've clustered the authors
into 2 clusters and 5 clusters.

>>>>

In Figure \ref{fig:authorcluster} we clustered developers using the
Ward method of Hierarchical clustering.  This diagram shows that
\texttt{petere}, \texttt{tgl} and \texttt{momjian} form their own
cluster (they are also the most frequent committers). This is
interesting because it means that the important developers are not
committing code that fits the same NFR profile. In terms of the larger
cluster we can see that \texttt{momjian} and \texttt{tgl} are in the
same cluster, but \texttt{petere} is not. The most frequent
committers do not share the same clusters. This implies that
developers do work on different sets of NFRs and have different
software quality focus.

Figure \ref{fig:authorcluster} clustered the authors into $2$ clusters
and $6$ clusters. We chose $6$ because the difference in width between
entities and centroids was minimal at $6$ and the derivative of was
the highest in that region as well.

It should be noted that much of PostgreSQL development originates from
the mailinglist and the developers are often pushing integrations.
